The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/method-of-moments.tex
Reworded moments using the terms central and raw

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
estimates for $\mu$, $\sigma$, and $\lambda$ using the method of moments, that
is, by comparing the first, second, and third moments about the mean (also
referred to as central moments) of $B$ and $Y$.

\subsection{The Moments of the Binomial Distribution}

Let's start with the binomial. The first two central moments are simply the
mean and variance:

@@

\subsection{The Moments of the Skew Normal Distribution}

>>>>

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
estimates for $\mu$, $\sigma$, and $\lambda$ using the method of moments, that
is, by comparing the first, second, and third moments about the mean (central
moments) of $B$ and $Y$.

\subsection{The Central Moments of the Binomial Distribution}

The first two central moments of the binomial are simply the mean and variance:

@@

\subsection{The Central Moments of the Skew Normal Distribution}
